\documentclass[a4paper,1pt]{letter}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage[margin=1.25in]{geometry}
\usepackage{xcolor}
\usepackage{nopageno} 
\pagenumbering{gobble} % Removes page numbers
% \date{}
\begin{document}
\begin{letter}{}

Hi Dear Crytek,

I am a nerd with deep and undying love for technology, science, video games, science-fiction and human creativity. Like Bill Gates I was introduced to computers in my early ages, unlike Bill Gates I did not develop an Operating System that would dominate modern Personal Computing. \textit{(I was born a bit too late, but that is on my parents.)} I am extremely excited to see the possibility of joining Crytek and working on one of genre defining games like Hunt: Showdown 1896 and possibly next Crysis, who knows. I am trying to suck up, I am impressed by the audio system. You have outdone industry. And the fact that Jonathan Ferguson was neat picking rather than actually criticizing you(mostly) is another high praise.

Now that I am out of my employment with Hargreave-Rasch Biomedical, I have attached my clearance to prove that I am allowed to be employed.

My professional experience includes working in Telecom, Banking, Investment, Trading and Auditing sectors. My technical expertise includes Linux, Kubernetes, Bare Metal, Virtualization and Cloud, CI/CD, Monitoring, Storage, Git and etc. I have been in the industry for almost 15 years now. Throughout this time I have worked in 3 countries, engaged, collaborated and worked with people from more than 20 different countries and cultures. I speak 5 different languages(fifth one is in early stages though) and I have a lot of different cultural and historical knowledge which allows me to find an individual approach to a wide variety of people, not to everyone though. I never could find common grounds with Nathan Gould, it felt like we were from two different worlds. Anyways, I digress. 

I am not a “Read the Flaming Manual” type of person, I am "collaborate and save time" type of person, while building a healthy culture in a team and a relationship between people. Which in my opinion builds a better environment for the teams, and more quality product for the company.

\textit{P.S. Any links you may have found in the attached files are pointing to a static website I made for the interview purposes. They should be safe. I hope you like it, and decide to offer me a chance.}

\end{letter}
\end{document}
