\documentclass{article}
\usepackage{geometry}
\geometry{margin=1in}
\title{\textbf{Special Investigative Report}}
\date{}

\begin{document}
	\pagestyle{empty}
	
	\maketitle
	
	\section*{Subject: Official Records and Investigation Findings}
	
	Official records consist of materials retrieved from the Hargreave-Rasch Biomedical Archive, the Karl Ernst Rasch residence, and the Jacob Hargreave residence, as well as documentation and witness statements obtained from Stillwater Bayou following its securement by U.S. Army forces.
	
	\section*{Background and Key Findings}
	
	Evidence suggests the individual of interest operated within Stillwater Bayou, conducting research activities circa 1890-1900s. Another researcher active in the area during this period was Dr. Philip Huff Jones, Director of the American Hunters Association and Superintendent of the Louisiana Asylum at Jackson. Dr. Jones, ultimately assassinated by Josie and Fina McGowan (alias "The Twins"), conducted unauthorized research involving human subjects. Although Dr. Jones and the subject of interest collaborated on research outcomes, direct partnership is unconfirmed, and there is no conclusive evidence the subject conducted human-based experiments. At a point thereafter, the subject departed Louisiana for Russia.
	
	\section*{Connections to Hargreave-Rasch Biomedical}
	
	Records indicate affiliations between the subject and Hargreave-Rasch Biomedical co-founders Karl Ernst Rasch and Jacob Hargreave, dating from the late 19th to early 20th century. These links span from Stillwater Bayou, Louisiana, to Tunguska, Russia. A cryptic invitation, bearing coordinates for the Tunguska incident site, was likely issued by the subject. Based on documentation recovered from Rasch’s personal and company archives, initial experimentation into controlled cellular mutation and integration of modified cells into living organisms was pioneered in Louisiana, heavily dependent on findings attributed to the subject of interest. Both Rasch and Hargreave appear to have theorized that the virus or entity affecting individuals in Stillwater Bayou originated from extraterrestrial lifeforms—referred to as the Ceph.
	
	\section*{Conclusion and Next Steps}
	
	Further investigation is ongoing to determine the subject’s activities following Rasch and Hargreave’s departure from Russia.
	
	\vspace{1cm}
	\noindent
	\textbf{Report submitted by:} \\
	Major Jack Reacher \\
	Chief Investigator \\
	U.S. Army 110th MP Special Investigations Unit
	
\end{document}