\documentclass{article}
\usepackage{geometry}
\geometry{margin=1in}
\title{\textbf{Investigative Report on Subject's Background and Employment Records}}
\author{Major Jack Reacher \\ Chief Investigator \\ U.S. Army 110th MP Special Investigations Unit}
\date{}

\begin{document}
\pagestyle{empty}

\maketitle

\section*{Subject: Background, Age Discrepancy, and Employment Records}

The subject is reportedly 32 years old, though evidence gathered indicates involvement or presence spanning back to the early last century, presenting inconsistencies in official records and raising questions regarding identity or longevity. Without further investigation, it is currently impossible to ascertain additional details with certainty.

\section*{Documented Evidence and Discrepancies}

We located a document within the HRB Archives in which a person bearing a similar name appears in records from the mid-1940s. The subject claimed this was merely a case of a different individual sharing the same name. However, an additional document corroborates that this individual is indeed the subject, citing a bureaucratic error in initial records. The subject appears unaware of this second document. We suspect that the "Mystery Man" marked on Mr. Rasch’s personal map may, in fact, refer to the subject's father.

\section*{Employment Records and Role}

Employment records confirm that the subject served as a Systems Engineer/Site Reliability Engineer with Hargreave-Rasch Biomedical, predominantly assigned to NanoSuit development. The subject reportedly had no direct involvement in biological research, including tests involving human subjects. Collaboration was limited to indirect support provided to Nathan Gould, assisting operatives “Prophet” (KIA) and “Alcatraz,” with no confirmed direct interaction with these operators.

\section*{Conclusion and Recommendations}

Due to current resource limitations, a deeper investigation is not feasible at this time. However, no immediate threat has been identified. It is recommended that the subject be cleared, though placed under continued observation.

\vspace{1cm}
\noindent
\textbf{Report submitted by:} \\
Major Jack Reacher \\
Chief Investigator \\
U.S. Army 110th MP Special Investigations Unit

\end{document}
